Multi-channel Kondo model URG

### 2021-11-07 multi-channel-urg.tex
pms limit

\documentclass{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
\numberwithin{equation}{section}
\allowdisplaybreaks
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Introduction}
The multi-channel Kondo model is described by the Hamiltonian
\begin{equation}\begin{aligned}
	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
\end{aligned}\end{equation}
It is mostly identical to the single-channel Kondo model: \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels. \(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors. The renormalization at step \(j\) is given by
\begin{equation}\begin{aligned}
	\Delta H_j = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c - T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
\end{aligned}\end{equation}
\begin{equation}\begin{aligned}
	c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, &&&H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
\end{aligned}\end{equation}
Usually we treat the \(\hat \omega\) as number(s) and study the renormalization in the couplings as functions of the quantum fluctuation scales. Each value of the fluctuation scale defines an eigendirection of \(\hat \omega\). We have then essentially traded off the complexity in the non-commutation of the diagonal and off-diagonal terms for all the directions in the manifold of \(\hat \omega\).

@@

\subsection{Total renormalization \(\Delta H^{(3)}\)}
Similar to the one-loop case, we will choose the require \(\omega\) and \(\omega^\prime\) to be related such that the  RG equations are \(\mathrm{Su}(2)\) symmetric; that is, we will require the terms that renormalize only \(S_d^z s^z\) vanish. The total renormalization at this order is obtained by adding eqs.~\ref{third_term_1} and \ref{third_term_2}.
\begin{equation}\begin{aligned}
	\Delta H^{(3)} = -\frac{J^3 K N_j n_j / 8}{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2}
\end{aligned}\end{equation}
Combining with \(\Delta H^{(2)}\), we get
\begin{equation}\begin{aligned}
	\Delta J = \frac{J^2 n_j \left[2 \left(D - 2\omega\right) - \frac{1}{4}J K N_j\right]}{\left(D - 2\omega\right)^2 - \frac{1}{4}J^2}
\end{aligned}\end{equation}

>>>>

\documentclass{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist,caption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Introduction}
The multi-channel Kondo model is described by the Hamiltonian
\begin{equation}\begin{aligned}
	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
\end{aligned}\end{equation}
It is mostly identical to the single-channel Kondo model: \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels. \(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors. The renormalization at step \(j\) is given by
\begin{equation}\begin{aligned}
	\Delta H_j = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c - T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
\end{aligned}\end{equation}
\begin{equation}\begin{aligned}
	c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, &&&H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
\end{aligned}\end{equation}
Usually we treat the \(\hat \omega\) as number(s) and study the renormalization in the couplings as functions of the quantum fluctuation scales. Each value of the fluctuation scale defines an eigendirection of \(\hat \omega\). We have then essentially traded off the complexity in the non-commutation of the diagonal and off-diagonal terms for all the directions in the manifold of \(\hat \omega\).

@@

\subsection{Total renormalization \(\Delta H^{(3)}\)}
Similar to the one-loop case, we will choose the require \(\omega\) and \(\omega^\prime\) to be related such that the  RG equations are \(\mathrm{Su}(2)\) symmetric; that is, we will require the terms that renormalize only \(S_d^z s^z\) vanish. The total renormalization at this order is obtained by adding eqs.~\ref{third_term_1} and \ref{third_term_2}.
\begin{equation}\begin{aligned}
	\Delta H^{(3)} = -\frac{J^3 K N_j n_j / 8}{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2}
\end{aligned}\end{equation}
Combining with \(\Delta H^{(2)}\), we get
\begin{equation}\begin{aligned}
	\Delta J = \frac{J^2 n_j \left[2 \left(D - 2\omega\right) - \frac{1}{2}J K N_j\right]}{\left(D - 2\omega\right)^2 - \frac{1}{4}J^2}
\end{aligned}\end{equation}
We choose \(\omega = -D/2\) to get a clearer idea of what the equations say. We also set \(N_j = \rho D\) and \(n_j = \rho |\delta D|\). Quantities with zero in the subscript will denote their values in the bare Hamiltonian. Using \(\delta D = -|\delta D|\), we can write the continuum form of the equation:
\begin{equation}\begin{aligned}
	\frac{\:\mathrm{d}J}{\:\mathrm{d}t} = \frac{J^2 \rho D^2 \left(1 - \frac{1}{8}JK\rho\right)}{D^2 - \frac{1}{16}J^2}
\end{aligned}\end{equation}
where \(dt = \frac{dD}{D}\).
\\\\
\begin{minipage}{0.45\textwidth}
For \(D \gg J\), we can ignore the \(J\) in the denominator, and the equation reduces to the one-loop poor man's scaling form
\begin{equation}\begin{aligned}
	\frac{\:\mathrm{d}J}{\:\mathrm{d}t} \simeq \frac{J^2 \rho D^2 \left(1 - \frac{1}{8}JK\rho\right)}{D^2} = J^2 \rho \left(1 - \frac{1}{8}JK\rho\right)
\end{aligned}\end{equation}
This equation has a stable fixed point at \(J^* = \frac{8}{\rho K}\).
\end{minipage}
\hfill
\begin{minipage}{0.45\textwidth}
	\includegraphics[width=\textwidth]{rg_flow_pms.pdf}
	\captionof{figure}{Attractive finite \(J\) fixed point of poor man scaling RG equation}
\end{minipage}

\(J_1^*,J_2^*\) are two critical points of the equation where either the numerator or the denominator changes sign: \(J_1^* = \frac{32 D_0}{K}, J_2^* = 4D\). In the thermodynamic limit, \(J_1^* \gg J\), so the numerator is always positive, and the flow of \(J\) is determined by the denominator. For \(J_0 < J_2^*\), \(J\) is relevant and flows up towards \(J_2^*\). On the other hand, if \(J_0 > J_2^*\), then we have an irrelevant coupling which again flows down towards \(J_2^*\)
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.5\textwidth]{./rg_flow.pdf}
	\caption{Attractive RG flows towards the stable intermediate coupling fixed point at \(J_1^*\).}
\end{figure}
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.8\textwidth]{./K=2,rel_and_irr.pdf}
	\caption{Attractive RG flows towards the stable intermediate coupling fixed point at \(J_1^*\).}
\end{figure}
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.4\textwidth]{./Jfp_vs_D.pdf}
	\caption{Variation of the fixed point value \(J^*\) against increasing bandwidth \(D_0\). The single-channel curve (red) keeps rising while the two-channel curve (blue) saturates to a finite value.}
\end{figure}
